Coding the LBG Wind (in 1D)

### 2010-08-28 Winds/papers/Theory/First/Notes/lbg_clumps.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5154 ac11df5e-a788-c23b-a8e1-c758c323924d

\documentclass[12pt,letterpaper]{article}

@@

So, is this at all plausible?  And, if not, can one monkey with the
size or $\Delta v_c$ of my clumps etc.\ to make a plausible scenario?

@@

>>>>

\documentclass[11pt,letterpaper]{article}

@@

@@

So, is this at all plausible?  And, if not, can one monkey with the
size or $\Delta v_c$ of my clumps etc.\ to make a plausible scenario?
It is evident that $M_{\rm TOT} \propto m_c / (\sigma \Delta v_c)$
where the $\Delta v_c$ comes in because that sets the size of each
shell.  I had worried that $(m_c / \sigma) \propto d_c$ but we are
demanding that each cloud is optically thick, i.e.\ $n_c d_c = {\rm
  Const}$.  Therefore, $m_c / \sigma = {\rm Const}$.  So all the
dependence is in $\Delta v_c$ and I don't see raising that by more
than a factor of a few.
